
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 7: Visualization - Some aspects of ggplot2"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2020_assignment7.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

**Questions**

Use the data of your own.  Produce the following types of plots and comment on each plot. Plots should be meaningful. If you use the data we used in class, make sure the plots are not the same as the ones in the slides. All plots should have title, caption, appropriate labels on x and y-axis. 
```{r}
library('tidyverse')
df <- read_csv('https://covidtracking.com/data/download/all-states-history.csv')
```

-------

1. Make a plot using `face_wrap` by one categorical variable (`face_wrap(~variable1)`)
```{r}
df %>% filter(state=='FL'|state=='SC') %>%
  ggplot(mapping=aes(x=deathIncrease, y=hospitalized))+
  geom_point()+
geom_smooth()+
facet_wrap(~state)+
labs(x= 'Increase in death',
     y='Hospitalized people',
     title = 'Scatter Plot of Increased deaths',
     caption = 'Florida has more hospitalized people')
```

2. Make a plot using `face_wrap` by two categorical variables (`face_wrap(variable1~variable2)`)
```{r}
df %>% filter(state=='MA'|state=='NY') %>%
  ggplot(mapping=aes(x=positiveIncrease, y=positive))+
  geom_point()+
  geom_smooth()+
  facet_wrap(dataQualityGrade~state)+
  labs(x= 'Increase in positive cases',
     y='Positive cases',
     title = 'Scatter Plot of Positive cases for each grade in MA and NY',
     caption = 'MA has more negative cases than NY')
```

3. Make a plot using `position ='jitter'`. 
```{r}
df %>% filter(state=='MA'|state=='NY') %>% ggplot()+
  geom_point(mapping=aes(x=negativeIncrease, y=negative),
            position='jitter')+
  labs(x= 'Increase in negative cases',
     y='Negative cases',
     title = 'Scatter Plot of Negative cases for each grade in MA and NY',
     caption = 'MA has more negative cases than NY')
```

4. Make a plot using `position ='dodge'`.
```{r}
df %>% filter(state=='ID') %>% ggplot()+
  geom_bar(mapping=aes(x=dataQualityGrade, fill=negative),
           position = 'dodge')+
  labs(x= 'Data Quality Grade',
     y='negative cases',
     title = 'Scatter Plot of Negative cases in Idaho',
     caption = 'Iadho has mostly A quality grade')
```

5. Make a plot using `position ='fill'`. 
```{r}
df %>% filter(state=='FL') %>% ggplot()+
  geom_bar(mapping=aes(x=dataQualityGrade, fill=negative),
           position = 'fill')+
  labs(x= 'Data Quality Grade',
     y='Negative cases',
     title = 'Bar plot of data quality grade in FL',
     caption = 'Florida has a negative results in all quality grades')
```

6. Make a plot using `geom_col`.
```{r}
df %>% group_by(dataQualityGrade) %>% summarise(mean=mean(negativeIncrease))%>%
  ggplot()+
  geom_col(mapping=aes(x=dataQualityGrade, y=mean))+
  labs(x= 'Data Quality Grade',
     y='Median negative cases for each grade',
     title = 'Bar Plot of Quality Grade',
     caption = 'A grade has the highest median')
```

7. Change the theme of one of your plots. 
```{r}
df %>% filter(state=='MA'|state=='RI') %>%
  ggplot(mapping=aes(x=positiveIncrease, y=positive, color=state))+
  geom_point()+
  geom_smooth()+
  facet_wrap(dataQualityGrade~state)+
  theme_dark()+
  labs(x= 'Increase in positive cases',
     y='Positive cases',
     title = 'Scatter Plot of Positive cases for each grade in MA and RI',
     caption = 'MA has more negative cases than RI')
```

8. Save a plot and put a link of the plot to your Github Webpage.  To link a plot `abc.png` you just need to insert the following on the README.md`
```{r}
df %>% group_by(dataQualityGrade) %>%
summarise(median=median(negativeIncrease)) %>% ggplot()+
  geom_col(mapping = aes(x=dataQualityGrade, y=median))+
  ggsave('abc.png')+ggsave('abc.pdf')+
  labs(x= 'dataQualityGrade',
     y='Median negative cases for each grade',
     title = 'Bar plot of quality grade',
     caption = 'A+ has the highest grade')
```

[Link to the image](000005.png)





